---
title: "bootcamp"
author: "Anna Yanchenko"
date: "8/21/2015"
output: html_document
---

Load the following packages for loading data ("curl"), data wrangling ("dplyr") and data visualization ("ggplot2").

`````{r}
library(curl)
library(dplyr)
library(ggplot2)
``````

Load the data
`````{r}
gap <- read.csv(curl("http://bit.ly/gap_data"))
`````

Example #1:
Subset and visualize.
```{r}
eu_52 <- gap %>%
  filter(continent == "Europe", year == 1952)
ggplot(data = eu_52, aes(x = gdpPercap, y = lifeExp)) +
  geom_point() 
```

Example #2:
```{r}
eu_5267 <- gap %>%
  filter(continent == "Europe", year %in% c(1952,1967))
ggplot(data = eu_5267, aes(x = gdpPercap, y = lifeExp, color = factor(year))) +
  geom_point() 
```


Example 3: Repeat exercises 1 and 2 with the new data set.
```{r}
gap_upd <- read.csv(curl("http://bit.ly/gap_data_upd"))
eu_52 <- gap %>%
  filter(continent == "Europe", year == 1952)
ggplot(data = eu_52, aes(x = gdpPercap, y = lifeExp)) +
  geom_point() 
eu_5267 <- gap %>%
  filter(continent == "Europe", year %in% c(1952,1967))
ggplot(data = eu_5267, aes(x = gdpPercap, y = lifeExp, color = factor(year))) +
  geom_point() 
```

